Simulating spaces and stressors

### 2024-04-22 Analysis/01_Simulating_spaces_and_stressors.Rmd
added letters

## First line
plot.text.box("Tree and trait\nsimulation:", cex = 2)
plot(simulated_data, main = "Tree and trait simulation\nunder a BM process (1D)", col = c("lightgrey", "blue"), ylab = "Trait 1")
plot(simulated_data, main = "Tree and trait simulation\nunder a BM process (2D)", col = c("lightgrey", "blue"), trait = c(1,2), xlab = "Trait 1", ylab = "Trait 2")

## Stressors
plot.text.box("1) Resampling\nwith stressor:\nnull mechanism", cex = 2)
plot.1D(trait_space, reduction = random_reduction, null = !random_reduction, main = "1D null mechanism")
plot.2D(trait_space, reduction = random_reduction, null = !random_reduction, main = "2D null mechanism")

plot.text.box("2) Resampling\nwith stressor:\nequalizing\nmechanism", cex = 2)
plot.1D(trait_space, reduction = equalizing_fitness, null = random_reduction, main = "1D equalising mechanism")
plot.2D(trait_space, reduction = equalizing_fitness, null = random_reduction, main = "2D equalising mechanism")

plot.text.box("3) Resampling\nwith stressor:\nfacilitating\nmechanism", cex = 2)
plot.1D(trait_space, reduction = facilitation, null = random_reduction, main = "1D facilitation mechanism")
plot.2D(trait_space, reduction = facilitation, null = random_reduction, main = "2D facilitation mechanism")

plot.text.box("4) Resampling\nwith stressor:\nfiltering\nmechanism", cex = 2)
plot.1D(trait_space, reduction = filtering_reduction, null = random_reduction, main = "1D filtering mechanism")
plot.2D(trait_space, reduction = filtering_reduction, null = random_reduction, main = "2D filtering mechanism")

plot.text.box("5) Resampling\nwith stressor:\ncompetition\nmechanism", cex = 2)
plot.1D(trait_space, reduction = !competitive_exclusion, null = random_reduction, main = "1D competition mechanism")
plot.2D(trait_space, reduction = !competitive_exclusion, null = random_reduction, main = "2D competition mechanism")

>>>>

## First line
plot.text.box("A) Tree and trait\nsimulation:", cex = 2)
plot(simulated_data, main = "Tree and trait simulation\nunder a BM process (1D)", col = c("lightgrey", "blue"), ylab = "Trait 1")
plot(simulated_data, main = "Tree and trait simulation\nunder a BM process (2D)", col = c("lightgrey", "blue"), trait = c(1,2), xlab = "Trait 1", ylab = "Trait 2")

## Stressors
plot.text.box("B) Resampling\nwith stressor:\nnull mechanism", cex = 2)
plot.1D(trait_space, reduction = random_reduction, null = !random_reduction, main = "1D null mechanism")
plot.2D(trait_space, reduction = random_reduction, null = !random_reduction, main = "2D null mechanism")

plot.text.box("C) Resampling\nwith stressor:\nequalizing\nmechanism", cex = 2)
plot.1D(trait_space, reduction = equalizing_fitness, null = random_reduction, main = "1D equalising mechanism")
plot.2D(trait_space, reduction = equalizing_fitness, null = random_reduction, main = "2D equalising mechanism")

plot.text.box("D) Resampling\nwith stressor:\nfacilitating\nmechanism", cex = 2)
plot.1D(trait_space, reduction = facilitation, null = random_reduction, main = "1D facilitation mechanism")
plot.2D(trait_space, reduction = facilitation, null = random_reduction, main = "2D facilitation mechanism")

plot.text.box("E) Resampling\nwith stressor:\nfiltering\nmechanism", cex = 2)
plot.1D(trait_space, reduction = filtering_reduction, null = random_reduction, main = "1D filtering mechanism")
plot.2D(trait_space, reduction = filtering_reduction, null = random_reduction, main = "2D filtering mechanism")

plot.text.box("F) Resampling\nwith stressor:\ncompetition\nmechanism", cex = 2)
plot.1D(trait_space, reduction = !competitive_exclusion, null = random_reduction, main = "1D competition mechanism")
plot.2D(trait_space, reduction = !competitive_exclusion, null = random_reduction, main = "2D competition mechanism")
